---
title: "PanelMatchSimulations"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Loading packages
```{r begin, results = 'hide', message=FALSE, warning=FALSE}
# clean slate
rm(list=ls())
options(digits=4)
# library(devtools)
# install_github("insongkim/wfe", ref = "new_branch")
# load packages
pkg <- c("wfe", "ggplot2", "plm", "pforeach", "scales")
lapply(pkg, require, character.only = TRUE)
setwd("/Users/EHW/Dropbox/w2fe/Simulations/results")
```

## Roadmap
This file reports simulation results for point estimates and coverage rate constructed with the following different methods:    
1. `PanelMatch` with weights supplied by synthetic control  
2. `PanelMatch` with weights supplied by Mahalanobis distance matching  
3. `PanelMatch` with weights supplied by propensity score matching  
4. OLS regression as a benchmark

## Simulation Set-up:  
The primary DGP is the following:  
$Y_{i,t} = \rho_{1}Y_{i, t-1} + \delta_{1}*X_{1i,t} + \omega_{1}*X_{2i,t} + \beta T_{it} + \tau_{1}*T_{i, t-1} + \alpha_{i} + \gamma_{t} + \epsilon_{it}$    
$T_{it} \sim Bernoulli(1 - \frac{P_{it}}{2})$    
$logit(P_{it}) = \rho_{2}*Y_{i, t-1} + \delta_{2}* X_{1it} + \omega_{2}*X_{2i,t} + \tau_{2}*T_{i, t-1} + \alpha_{i} + \gamma_{t}$   
$X_{1it} = .75* X_{1i,t-1} + \alpha_{i} + \gamma_{t} + z_{it}$  
$\alpha_{i} \sim Normal(\mu = 4, \sigma^{2} = 1)$   
$\gamma_{t} \sim Normal(\mu = 4, \sigma^{2} = 1)$  
$\epsilon_{it} = \phi_{e} * \epsilon_{i, t-1} + u_{it}$  
$u_{it} \sim Normal(\mu = 0, \sigma^{2} = unif(0,1))$   

The true treatment effect is $\beta = 1$. We let $\rho_{1} = \rho_{2} = 0.8$, effectively letting the outcome at $t-1$ be highly correlated with both outcome at $t$ and treatment at $t$. We set $\delta_{1} = \delta_{2} = 0.4$ so that both outcome and treatment at $t$ are affected by a continuous covariate, $X_{1}$, to some extent. $X_{1}$ is also serially correlated itself. We let $\omega_{1} = \omega_{2} = 0$, so that another covariate $X_{2}$ is not going to affect our data generating process at all for either outcome or treatment. We let $\tau_{1} = \tau_{2} = 0$, so that neither the outcome nor treatment at $t$ is affected by treatment at $t-1$.  
In other words, this data generating process stipulates that the current outcome is affected by both past outcome and current treatment, and current treatment itself is also affected by past outcome. Both treatment and outcome are also affected by a continuous covariate and two-way fixed effects. Note that we make the error structure both heteroskedastic, by allowing the variance of $u$ to follow a uniform distribution, and serially corrleated, by setting $\phi_{e} = 0.5$.  
For each simulation, we will compute WFE regression standard errors. We try $M = 1$ for Mahalanobis and propensity score matching throughout the simulation, but try both $L = 6$ and $L = 4$ for lag length. 


```{r simulation_code,  message=FALSE, warning=FALSE, cache= TRUE, echo = FALSE, eval=FALSE}
sim_wfe2 <- function (N = 100, Time = 20, lag.one = 4, lag.two = 6,
                      lead = 0,
                      rho_1 = .8, rho_t_1 = .8, rho_tt_1 = .2, 
                      rho_x = .4, rho_x2 = 0, lagTreOutc = .2, 
                      beta = 1, beta_x = .2, beta_x2 = 0, 
                      phi = .75, rho_t_2 = .3, ephi = .5,
                      rho_2 = .3, M = 1, hetereo = T,
                      ITER = 1000) {
  y <- matrix(NA, ncol = N, nrow = Time)
  eps <- matrix(NA, ncol = N, nrow = Time)
  treat <- matrix(NA, ncol = N, nrow = Time)
  y.lagged <- matrix(NA, ncol = N, nrow = Time)
  treat.lagged <- matrix(NA, ncol = N, nrow = Time)
  
  alphai <- rnorm(N, mean = 4)
  gammat <- rnorm(Time, mean = 4)
  
  x <- matrix(rep(NA, N*Time), ncol = N)
  for (i in 1:N) {
    x[1, i] <- rnorm(1, 0.5, 1) + gammat[1]
    for(t in 2:Time){
      x[t, i] <- phi*x[t-1, i] + rnorm(1, 0.5, 1) + gammat[t] + alphai[i]
    }
    
  }
  
  x2 <- matrix(rep(NA, N*Time), ncol = N)
  for (i in 1:N) {
    x2[1, i] <- rnorm(1, 0.5, 1) + gammat[1]
    for(t in 2:Time){
      x2[t, i] <- phi*x2[t-1, i] + rnorm(1, 0.5, 1) + gammat[t] + alphai[i]
    }
    
  }
  
  for (i in 1:N) {
    y.lagged[1, i] <- rnorm(1) + alphai[i] + gammat[1]
    treat.lagged[1,i] <- rbinom(1,1,exp(rho_x*x[1,i] + rho_x2*x2[1,i] + alphai[i] + gammat[1])/(1+exp(rho_x*x[1,i] + rho_x2*x2[1,i] + alphai[i] + gammat[1])))
    # think about commenting out treat.error
    # treat.error <- -4 #rnorm(1,-4)
    prob <- exp(rho_t_1*y.lagged[1,i] + alphai[i] + rho_tt_1*treat.lagged[1,i] + rho_x*x[1,i] + rho_x2*x2[1,i] + gammat[1])/
      (1+exp(rho_t_1*y.lagged[1,i] + alphai[i] + rho_tt_1*treat.lagged[1,i] + rho_x*x[1,i] + rho_x2*x2[1,i] + gammat[1]))
    treat[1,i] <- rbinom(1,1, prob/2)
    eps[1, i] <- rnorm(1)
    y[1,i] <- rho_1*y.lagged[1,i] + alphai[i] + gammat[1] + 
      beta*treat[1,i] + lagTreOutc*treat.lagged[1,i] + beta_x*x[1,i] + beta_x2*x2[1,i] +
      eps[1,i]
    
    for (t in 2:Time) {
      # treat.error <- -4 #rnorm(1,-4)
      prob <- exp(rho_t_1*y[t-1,i] + alphai[i] + rho_tt_1*treat[t-1,i] + rho_x*x[t,i] + rho_x2*x2[t,i] +gammat[t])/
        (1+exp(rho_t_1*y[t-1,i] + alphai[i] + rho_tt_1*treat[t-1,i] + rho_x*x[t,i] + rho_x2*x2[t,i] + gammat[t]))
      treat[t,i] <- rbinom(1,1, prob/2)
      treat.lagged[t,i] <- treat[t-1,i]
      
      if(hetereo == T) {
        eps[t, i] <- ephi*eps[t-1, i] + rnorm(n = 1, mean = 0, sd = runif(1, 0, 1))
      } else {
        eps[t, i] <- ephi*eps[t-1, i] + rnorm(n = 1, mean = 0, sd = 1)
      }
      
      # truth:
      y[t, i] <- rho_1*y[t-1, i] + beta*treat[t,i] + lagTreOutc*treat[t-1,i] + beta_x*x[t,i] + beta_x2*x2[t,i] + 
        alphai[i] + gammat[t] + eps[t, i] # the current period
      
      y.lagged[t,i] <- y[t-1,i]
    }
    
  }
  y.vec <- c(y)
  y.lagged.vec <- c(y.lagged)
  treat.vec <- c(treat)
  treat.lagged.vec <- c(treat.lagged)
  x.vec <- c(x)
  #y2.vec <- c(y2)
  ## generate unit and time index
  unit.index <- rep(1:N, each = Time)
  time.index <- rep(1:Time, N)
  # Data.str <- as.data.frame(cbind(y.vec, treat.vec, unit.index, x1.vec, x2.vec))
  # colnames(Data.str) <- c("y", "tr", "strata.id", "x1", "x2")
  Data.obs <- as.data.frame(cbind(time.index, unit.index, y.vec, y.lagged.vec,
                                  treat.vec, treat.lagged.vec, x.vec))
  colnames(Data.obs) <- c("time", "unit", "y", "y_l1", "treat", "treat_l1", "x")
  ##### L = 4
  ### Correct Models:
  ## matched sets
  cat("\n ----------------------- \n")
  cat("Matches_Maha_lag.one \n")
  cat("\n ----------------------- \n")
  Matches_Maha_lag.one <- tryCatch(PanelMatch(lag = lag.one, max.lead = lead, time.id = "time", 
                                              unit.id = "unit",
                                              treatment = "treat", 
                                              formula = y~treat + x, 
                                              method = "Maha",
                                              qoi = "ate", M = M,
                                              data = Data.obs), 
                                   error = function(err) NA)
  
  cat("\n ----------------------- \n")
  cat("Matches_Pscore_lag.one \n")
  cat("\n ----------------------- \n")
  
  Matches_Pscore_lag.one <- tryCatch(PanelMatch(lag = lag.one, max.lead = lead, time.id = "time", 
                                                unit.id = "unit",
                                                treatment = "treat", formula = y ~ treat + x, 
                                                method = "Pscore",
                                                qoi = "ate", M = M,
                                                data = Data.obs),
                                     error = function(err) NA)
  
  cat("\n ----------------------- \n")
  cat("Matches_Synth_lag.one \n")
  cat("\n ----------------------- \n")
  Matches_Synth_lag.one <- tryCatch(PanelMatch(lag = lag.one, max.lead = lead, time.id = "time", 
                                               unit.id = "unit",
                                               treatment = "treat", formula = y ~ treat + x, 
                                               method = "Synth",
                                               qoi = "ate", 
                                               data = Data.obs),
                                    error = function(err) NA)
  
  
  cat("\n ----------------------- \n")
  cat("Synth_wfe_lag.one \n")
  cat("\n ----------------------- \n")
  
  ### PanelEstimate ###
  Synth_wfe_lag.one <- tryCatch(PanelEstimate_tmp2(lead = lead, 
                                                   inference = "wfe",
                                                   matched_sets = Matches_Synth_lag.one),
                                error = function(err) NA)
  
  
  cat("\n ----------------------- \n")
  cat("Maha_wfe_lag.one \n")
  cat("\n ----------------------- \n")
  
  Maha_wfe_lag.one <- tryCatch(PanelEstimate_tmp2(lead = lead, inference = "wfe",
                                                  matched_sets = Matches_Maha_lag.one),
                               error = function(err) NA)
  
  
  
  cat("\n ----------------------- \n")
  cat("Pscore_wfe_lag.one \n")
  cat("\n ----------------------- \n")
  
  Pscore_wfe_lag.one <- tryCatch(PanelEstimate_tmp2(lead = lead, 
                                                    inference = "wfe",
                                                    matched_sets = Matches_Pscore_lag.one),
                                 error = function(err) NA)
  
  ##### L = 6
  ### Correct Models:
  ## matched sets
  
  cat("\n ----------------------- \n")
  cat("Matches_Maha_lag.two \n")
  cat("\n ----------------------- \n")
  
  Matches_Maha_lag.two <- tryCatch(PanelMatch(lag = lag.two, max.lead = lead, time.id = "time", 
                                              unit.id = "unit",
                                              treatment = "treat", 
                                              formula = y~treat + x, 
                                              method = "Maha",
                                              qoi = "ate", M = M,
                                              data = Data.obs), 
                                   error = function(err) NA)
  
  cat("\n ----------------------- \n")
  cat("Matches_Pscore_lag.two \n")
  cat("\n ----------------------- \n")
  
  
  Matches_Pscore_lag.two <- tryCatch(PanelMatch(lag = lag.two, max.lead = lead, time.id = "time", 
                                                unit.id = "unit",
                                                treatment = "treat", formula = y ~ treat + x, 
                                                method = "Pscore",
                                                qoi = "ate", M = M,
                                                data = Data.obs),
                                     error = function(err) NA)
  
  cat("\n ----------------------- \n")
  cat("Matches_Synth_lag.two \n")
  cat("\n ----------------------- \n")
  
  Matches_Synth_lag.two <- tryCatch(PanelMatch(lag = lag.two, max.lead = lead, time.id = "time", 
                                               unit.id = "unit",
                                               treatment = "treat", formula = y ~ treat + x, 
                                               method = "Synth",
                                               qoi = "ate", 
                                               data = Data.obs),
                                    error = function(err) NA)
  
  
  ### PanelEstimate ###
  
  cat("\n ----------------------- \n")
  cat("Synth_wfe_lag.two \n")
  cat("\n ----------------------- \n")
  
  Synth_wfe_lag.two <- tryCatch(PanelEstimate_tmp2(lead = lead, 
                                                   inference = "wfe",
                                                   matched_sets = Matches_Synth_lag.two),
                                error = function(err) NA)
  
  
  cat("\n ----------------------- \n")
  cat("Maha_wfe_lag.two \n")
  cat("\n ----------------------- \n")
  
  Maha_wfe_lag.two <- tryCatch(PanelEstimate_tmp2(lead = lead, inference = "wfe",
                                                  matched_sets = Matches_Maha_lag.two),
                               error = function(err) NA)
  
  cat("\n ----------------------- \n")
  cat("Pscore_wfe_lag.two \n")
  cat("\n ----------------------- \n")
  
  Pscore_wfe_lag.two <- tryCatch(PanelEstimate_tmp2(lead = lead, 
                                                    inference = "wfe",
                                                    matched_sets = Matches_Pscore_lag.two),
                                 error = function(err) NA)
  
  
  cat("\n ----------------------- \n")
  cat("ols \n")
  cat("\n ----------------------- \n")
  if(rho_tt_1 == 0 & lagTreOutc == 0) {
    ols <- tryCatch(plm(y~treat + y_l1 + x, 
                        index = c("unit","time"), model = "within", 
                        effect = "twoways",
                        data = Data.obs), error = function(err) NA)
  } else {
    ols <- tryCatch(plm(y~treat + y_l1 + treat_l1 + x, 
                        index = c("unit","time"), model = "within", 
                        effect = "twoways",
                        data = Data.obs), error = function(err) NA)
  }
  
  
  cat("\n ----------------------- \n")
  cat("summarizing stuff \n")
  cat("\n ----------------------- \n")
  
  Synth_wfe_lag.one_se  <- tryCatch(Synth_wfe_lag.one$se, error = function(err) NA)
  Synth_wfe_lag.one_coef  <- tryCatch(Synth_wfe_lag.one$coefficients[1], error = function(err) NA)
  
  Maha_wfe_lag.one_se  <- tryCatch(Maha_wfe_lag.one$se, error = function(err) NA)
  Maha_wfe_lag.one_coef  <- tryCatch(Maha_wfe_lag.one$coefficients[1], error = function(err) NA)
  
  Pscore_wfe_lag.one_se  <- tryCatch(Pscore_wfe_lag.one$se, error = function(err) NA)
  Pscore_wfe_lag.one_coef  <- tryCatch(Pscore_wfe_lag.one$coefficients[1], error = function(err) NA)
  
  Synth_wfe_lag.two_se  <- tryCatch(Synth_wfe_lag.two$se, error = function(err) NA)
  Synth_wfe_lag.two_coef  <- tryCatch(Synth_wfe_lag.two$coefficients[1], error = function(err) NA)
  
  Maha_wfe_lag.two_se  <- tryCatch(Maha_wfe_lag.two$se, error = function(err) NA)
  Maha_wfe_lag.two_coef  <- tryCatch(Maha_wfe_lag.two$coefficients[1], error = function(err) NA)
  
  Pscore_wfe_lag.two_se  <- tryCatch(Pscore_wfe_lag.two$se, error = function(err) NA)
  Pscore_wfe_lag.two_coef  <- tryCatch(Pscore_wfe_lag.two$coefficients[1], error = function(err) NA)
  
  ols_coef  <- tryCatch(ols$coefficients[1], error = function(err) NA)
  ols_se  <- tryCatch(sqrt(ols$vcov["treat", "treat"]), error = function(err) NA)
  
  return(list("Synth_wfe_lag.one_se" = Synth_wfe_lag.one_se,
              "Synth_wfe_lag.one_coef" = Synth_wfe_lag.one_coef,
              
              "Maha_wfe_lag.one_se" = Maha_wfe_lag.one_se,
              "Maha_wfe_lag.one_coef" = Maha_wfe_lag.one_coef,
              
              "Pscore_wfe_lag.one_se" = Pscore_wfe_lag.one_se,
              "Pscore_wfe_lag.one_coef" = Pscore_wfe_lag.one_coef,
              
              "Synth_wfe_lag.two_se" = Synth_wfe_lag.two_se,
              "Synth_wfe_lag.two_coef" = Synth_wfe_lag.two_coef,
              
              "Maha_wfe_lag.two_se" = Maha_wfe_lag.two_se,
              "Maha_wfe_lag.two_coef" = Maha_wfe_lag.two_coef,
              
              "Pscore_wfe_lag.two_se" = Pscore_wfe_lag.two_se,
              "Pscore_wfe_lag.two_coef" = Pscore_wfe_lag.two_coef,
              
              "ols_coef" = ols_coef,
              "ols_se" = ols_se
              # "ols_coef_mis" = ols_coef_mis,
              # "ols_se_mis" = ols_se_mis,
              # "gmm_d_coef" = gmm_d_coef,
              # "gmm_d_se" = gmm_d_se,
              # "gmm_s_coef" = gmm_s_coef,
              # "gmm_s_se" = gmm_s_se
              # "gmm_d_mis_coef" = gmm_d_mis_coef,
              # "gmm_d_mis_se" = gmm_d_mis_se,
              # "gmm_s_mis_coef" = gmm_s_mis_coef,
              # "gmm_s_mis_se" = gmm_s_mis_se
  ))
  
}
```

## Results
We report percentage of point estimation bias for $N = 50$, $N = 100$ and $N = 200$. This percentage is calculated as $100*\frac{|\frac{1}{B}\sum^{B}_{b=1} \hat{\beta}_{b} - \beta|}{\beta}$, where $\beta = 1$ and $B = 1000$ is the number of simulations. Overall, our methods recover the truth very well even for $N = 50$. Note that OLS in this case also performs quite well, indicating that the Nickell bias is likely to be tiny in our data generating process when $T = 20$. Nevertheless, our methods still **_substantially outperform_** OLS as $N$ grows larger.  

```{r echo = FALSE, results = 'hide', cache=TRUE, message = FALSE}
# 
setwd("/Users/EHW/Dropbox/w2fe/Simulations/results")
load("New_N50_ephi0.5_T20_hetereo") 
load("New_N100_ephi0.5_T20_hetereo") 
load("New_N200_ephi0.5_T20_hetereo") 

# N = 50
ols_coef_50 <- percent(abs(1-mean(sapply(New_N50_ephi0.5_T20_hetereo, function (x) x$ols_coef), na.rm = T)))
Synth_wfe_lag.one_coef_50 <- percent(abs(1-mean(sapply(New_N50_ephi0.5_T20_hetereo, 
                                               function (x) x$Synth_wfe_lag.one_coef), na.rm = T)))
Maha_wfe_lag.one_coef_50 <- percent(abs(1-mean(sapply(New_N50_ephi0.5_T20_hetereo, 
                                               function (x) x$Maha_wfe_lag.one_coef), na.rm = T)))

Pscore_wfe_lag.one_coef_50 <- percent(abs(1-mean(sapply(New_N50_ephi0.5_T20_hetereo, 
                                               function (x) x$Pscore_wfe_lag.one_coef), na.rm = T)))

Synth_wfe_lag.two_coef_50 <- percent(abs(1-mean(sapply(New_N50_ephi0.5_T20_hetereo, 
                                               function (x) x$Synth_wfe_lag.two_coef), na.rm = T)))
Maha_wfe_lag.two_coef_50 <- percent(abs(1-mean(sapply(New_N50_ephi0.5_T20_hetereo, 
                                              function (x) x$Maha_wfe_lag.two_coef), na.rm = T)))

Pscore_wfe_lag.two_coef_50 <- percent(abs(1-mean(sapply(New_N50_ephi0.5_T20_hetereo, 
                                                function (x) x$Pscore_wfe_lag.two_coef), na.rm = T)))

# N = 100
ols_coef_100 <- percent(abs(1-mean(sapply(New_N100_ephi0.5_T20_hetereo, function (x) x$ols_coef), na.rm = T)))
Synth_wfe_lag.one_coef_100 <- percent(abs(1-mean(sapply(New_N100_ephi0.5_T20_hetereo, 
                                               function (x) x$Synth_wfe_lag.one_coef), na.rm = T)))
Maha_wfe_lag.one_coef_100 <- percent(abs(1-mean(sapply(New_N100_ephi0.5_T20_hetereo, 
                                               function (x) x$Maha_wfe_lag.one_coef), na.rm = T)))

Pscore_wfe_lag.one_coef_100 <- percent(abs(1-mean(sapply(New_N100_ephi0.5_T20_hetereo, 
                                               function (x) x$Pscore_wfe_lag.one_coef), na.rm = T)))

Synth_wfe_lag.two_coef_100 <- percent(abs(1-mean(sapply(New_N100_ephi0.5_T20_hetereo, 
                                               function (x) x$Synth_wfe_lag.two_coef), na.rm = T)))
Maha_wfe_lag.two_coef_100 <- percent(abs(1-mean(sapply(New_N100_ephi0.5_T20_hetereo, 
                                              function (x) x$Maha_wfe_lag.two_coef), na.rm = T)))

Pscore_wfe_lag.two_coef_100 <- percent(abs(1-mean(sapply(New_N100_ephi0.5_T20_hetereo, 
                                                function (x) x$Pscore_wfe_lag.two_coef), na.rm = T)))

# N = 200
ols_coef_200 <- percent(abs(1-mean(sapply(New_N200_ephi0.5_T20_hetereo, function (x) x$ols_coef), na.rm = T)))
Synth_wfe_lag.one_coef_200 <- percent(abs(1-mean(sapply(New_N200_ephi0.5_T20_hetereo, 
                                               function (x) x$Synth_wfe_lag.one_coef), na.rm = T)))
Maha_wfe_lag.one_coef_200 <- percent(abs(1-mean(sapply(New_N200_ephi0.5_T20_hetereo, 
                                               function (x) x$Maha_wfe_lag.one_coef), na.rm = T)))

Pscore_wfe_lag.one_coef_200 <- percent(abs(1-mean(sapply(New_N200_ephi0.5_T20_hetereo, 
                                               function (x) x$Pscore_wfe_lag.one_coef), na.rm = T)))

Synth_wfe_lag.two_coef_200 <- percent(abs(1-mean(sapply(New_N200_ephi0.5_T20_hetereo, 
                                               function (x) x$Synth_wfe_lag.two_coef), na.rm = T)))
Maha_wfe_lag.two_coef_200 <- percent(abs(1-mean(sapply(New_N200_ephi0.5_T20_hetereo, 
                                              function (x) x$Maha_wfe_lag.two_coef), na.rm = T)))

Pscore_wfe_lag.two_coef_200 <- percent(abs(1-mean(sapply(New_N200_ephi0.5_T20_hetereo, 
                                                function (x) x$Pscore_wfe_lag.two_coef), na.rm = T)))

parameters <- c("Synth L = 4", "Synth L = 6", "Maha L = 4", "Maha L =6",
                "Pscore L = 4", "Pscore L = 6", "OLS")
N50 <- c(Synth_wfe_lag.one_coef_50, Synth_wfe_lag.two_coef_50, 
         Maha_wfe_lag.one_coef_50, Maha_wfe_lag.two_coef_50,
         Pscore_wfe_lag.one_coef_50, Pscore_wfe_lag.two_coef_50,
         ols_coef_50)

N100 <- c(Synth_wfe_lag.one_coef_100, Synth_wfe_lag.two_coef_100, 
         Maha_wfe_lag.one_coef_100, Maha_wfe_lag.two_coef_100,
         Pscore_wfe_lag.one_coef_100, Pscore_wfe_lag.two_coef_100,
         ols_coef_100)

N200 <- c(Synth_wfe_lag.one_coef_200, Synth_wfe_lag.two_coef_200, 
         Maha_wfe_lag.one_coef_200, Maha_wfe_lag.two_coef_200,
         Pscore_wfe_lag.one_coef_200, Pscore_wfe_lag.two_coef_200,
         ols_coef_200)

```

### Bias in Point Estimate
```{R, echo = FALSE, cache = TRUE}
table_pe <- as.data.frame(cbind(parameters, N50, N100, N200))
library(knitr)
kable(table_pe)
```

```{R coverage, echo = FALSE, cache = TRUE}
# N = 50

coverage_Synth_wfe_lag.one_N50 <- rep(NA, length(New_N50_ephi0.5_T20_hetereo))
for (i in 1:length(New_N50_ephi0.5_T20_hetereo)) {
  if (New_N50_ephi0.5_T20_hetereo[[i]]$Synth_wfe_lag.one_coef- New_N50_ephi0.5_T20_hetereo[[i]]$Synth_wfe_lag.one_se * qnorm(.95) < 1 &
      New_N50_ephi0.5_T20_hetereo[[i]]$Synth_wfe_lag.one_coef + New_N50_ephi0.5_T20_hetereo[[i]]$Synth_wfe_lag.one_se * qnorm(.95) > 1) {
    coverage_Synth_wfe_lag.one_N50[i] <- 1
  } else {
    coverage_Synth_wfe_lag.one_N50[i] <- 0
  }
  
}
coverage_Synth_wfe_lag.one_N50 <- percent(mean(coverage_Synth_wfe_lag.one_N50))


coverage_Synth_wfe_lag.two_N50 <- rep(NA, length(New_N50_ephi0.5_T20_hetereo))
for (i in 1:length(New_N50_ephi0.5_T20_hetereo)) {
  if (New_N50_ephi0.5_T20_hetereo[[i]]$Synth_wfe_lag.two_coef- New_N50_ephi0.5_T20_hetereo[[i]]$Synth_wfe_lag.two_se * qnorm(.95) < 1 &
      New_N50_ephi0.5_T20_hetereo[[i]]$Synth_wfe_lag.two_coef + New_N50_ephi0.5_T20_hetereo[[i]]$Synth_wfe_lag.two_se * qnorm(.95) > 1) {
    coverage_Synth_wfe_lag.two_N50[i] <- 1
  } else {
    coverage_Synth_wfe_lag.two_N50[i] <- 0
  }
  
}
coverage_Synth_wfe_lag.two_N50 <- percent(mean(coverage_Synth_wfe_lag.two_N50))



coverage_Maha_wfe_lag.one_N50 <- rep(NA, length(New_N50_ephi0.5_T20_hetereo))
for (i in 1:length(New_N50_ephi0.5_T20_hetereo)) {
  if (New_N50_ephi0.5_T20_hetereo[[i]]$Maha_wfe_lag.one_coef- New_N50_ephi0.5_T20_hetereo[[i]]$Maha_wfe_lag.one_se * qnorm(.95) < 1 &
      New_N50_ephi0.5_T20_hetereo[[i]]$Maha_wfe_lag.one_coef + New_N50_ephi0.5_T20_hetereo[[i]]$Maha_wfe_lag.one_se * qnorm(.95) > 1) {
    coverage_Maha_wfe_lag.one_N50[i] <- 1
  } else {
    coverage_Maha_wfe_lag.one_N50[i] <- 0
  }
  
}
coverage_Maha_wfe_lag.one_N50 <- percent(mean(coverage_Maha_wfe_lag.one_N50))


coverage_Maha_wfe_lag.two_N50 <- rep(NA, length(New_N50_ephi0.5_T20_hetereo))
for (i in 1:length(New_N50_ephi0.5_T20_hetereo)) {
  if (New_N50_ephi0.5_T20_hetereo[[i]]$Maha_wfe_lag.two_coef- New_N50_ephi0.5_T20_hetereo[[i]]$Maha_wfe_lag.two_se * qnorm(.95) < 1 &
      New_N50_ephi0.5_T20_hetereo[[i]]$Maha_wfe_lag.two_coef + New_N50_ephi0.5_T20_hetereo[[i]]$Maha_wfe_lag.two_se * qnorm(.95) > 1) {
    coverage_Maha_wfe_lag.two_N50[i] <- 1
  } else {
    coverage_Maha_wfe_lag.two_N50[i] <- 0
  }
  
}
coverage_Maha_wfe_lag.two_N50 <- percent(mean(coverage_Maha_wfe_lag.two_N50))


coverage_Pscore_wfe_lag.one_N50 <- rep(NA, length(New_N50_ephi0.5_T20_hetereo))
for (i in 1:length(New_N50_ephi0.5_T20_hetereo)) {
  if (New_N50_ephi0.5_T20_hetereo[[i]]$Pscore_wfe_lag.one_coef- New_N50_ephi0.5_T20_hetereo[[i]]$Pscore_wfe_lag.one_se * qnorm(.95) < 1 &
      New_N50_ephi0.5_T20_hetereo[[i]]$Pscore_wfe_lag.one_coef + New_N50_ephi0.5_T20_hetereo[[i]]$Pscore_wfe_lag.one_se * qnorm(.95) > 1) {
    coverage_Pscore_wfe_lag.one_N50[i] <- 1
  } else {
    coverage_Pscore_wfe_lag.one_N50[i] <- 0
  }
  
}
coverage_Pscore_wfe_lag.one_N50 <- percent(mean(coverage_Pscore_wfe_lag.one_N50))


coverage_Pscore_wfe_lag.two_N50 <- rep(NA, length(New_N50_ephi0.5_T20_hetereo))
for (i in 1:length(New_N50_ephi0.5_T20_hetereo)) {
  if (New_N50_ephi0.5_T20_hetereo[[i]]$Pscore_wfe_lag.two_coef- New_N50_ephi0.5_T20_hetereo[[i]]$Pscore_wfe_lag.two_se * qnorm(.95) < 1 &
      New_N50_ephi0.5_T20_hetereo[[i]]$Pscore_wfe_lag.two_coef + New_N50_ephi0.5_T20_hetereo[[i]]$Pscore_wfe_lag.two_se * qnorm(.95) > 1) {
    coverage_Pscore_wfe_lag.two_N50[i] <- 1
  } else {
    coverage_Pscore_wfe_lag.two_N50[i] <- 0
  }
  
}
coverage_Pscore_wfe_lag.two_N50 <- percent(mean(coverage_Pscore_wfe_lag.two_N50))

coverage_ols_N50 <- rep(NA, length(New_N50_ephi0.5_T20_hetereo))
for (i in 1:length(New_N50_ephi0.5_T20_hetereo)) {
  if (New_N50_ephi0.5_T20_hetereo[[i]]$ols_coef- New_N50_ephi0.5_T20_hetereo[[i]]$ols_se * qnorm(.95) < 1 &
      New_N50_ephi0.5_T20_hetereo[[i]]$ols_coef + New_N50_ephi0.5_T20_hetereo[[i]]$ols_se * qnorm(.95) > 1) {
    coverage_ols_N50[i] <- 1
  } else {
    coverage_ols_N50[i] <- 0
  }
  
}
coverage_ols_N50 <- percent(mean(coverage_ols_N50))


## N = 100
coverage_Synth_wfe_lag.one_N100 <- rep(NA, length(New_N100_ephi0.5_T20_hetereo))
for (i in 1:length(New_N100_ephi0.5_T20_hetereo)) {
  if (New_N100_ephi0.5_T20_hetereo[[i]]$Synth_wfe_lag.one_coef- New_N100_ephi0.5_T20_hetereo[[i]]$Synth_wfe_lag.one_se * qnorm(.95) < 1 &
      New_N100_ephi0.5_T20_hetereo[[i]]$Synth_wfe_lag.one_coef + New_N100_ephi0.5_T20_hetereo[[i]]$Synth_wfe_lag.one_se * qnorm(.95) > 1) {
    coverage_Synth_wfe_lag.one_N100[i] <- 1
  } else {
    coverage_Synth_wfe_lag.one_N100[i] <- 0
  }
  
}
coverage_Synth_wfe_lag.one_N100 <- percent(mean(coverage_Synth_wfe_lag.one_N100))


coverage_Synth_wfe_lag.two_N100 <- rep(NA, length(New_N100_ephi0.5_T20_hetereo))
for (i in 1:length(New_N100_ephi0.5_T20_hetereo)) {
  if (New_N100_ephi0.5_T20_hetereo[[i]]$Synth_wfe_lag.two_coef- New_N100_ephi0.5_T20_hetereo[[i]]$Synth_wfe_lag.two_se * qnorm(.95) < 1 &
      New_N100_ephi0.5_T20_hetereo[[i]]$Synth_wfe_lag.two_coef + New_N100_ephi0.5_T20_hetereo[[i]]$Synth_wfe_lag.two_se * qnorm(.95) > 1) {
    coverage_Synth_wfe_lag.two_N100[i] <- 1
  } else {
    coverage_Synth_wfe_lag.two_N100[i] <- 0
  }
  
}
coverage_Synth_wfe_lag.two_N100 <- percent(mean(coverage_Synth_wfe_lag.two_N100))



coverage_Maha_wfe_lag.one_N100 <- rep(NA, length(New_N100_ephi0.5_T20_hetereo))
for (i in 1:length(New_N100_ephi0.5_T20_hetereo)) {
  if (New_N100_ephi0.5_T20_hetereo[[i]]$Maha_wfe_lag.one_coef- New_N100_ephi0.5_T20_hetereo[[i]]$Maha_wfe_lag.one_se * qnorm(.95) < 1 &
      New_N100_ephi0.5_T20_hetereo[[i]]$Maha_wfe_lag.one_coef + New_N100_ephi0.5_T20_hetereo[[i]]$Maha_wfe_lag.one_se * qnorm(.95) > 1) {
    coverage_Maha_wfe_lag.one_N100[i] <- 1
  } else {
    coverage_Maha_wfe_lag.one_N100[i] <- 0
  }
  
}
coverage_Maha_wfe_lag.one_N100 <- percent(mean(coverage_Maha_wfe_lag.one_N100))


coverage_Maha_wfe_lag.two_N100 <- rep(NA, length(New_N100_ephi0.5_T20_hetereo))
for (i in 1:length(New_N100_ephi0.5_T20_hetereo)) {
  if (New_N100_ephi0.5_T20_hetereo[[i]]$Maha_wfe_lag.two_coef- New_N100_ephi0.5_T20_hetereo[[i]]$Maha_wfe_lag.two_se * qnorm(.95) < 1 &
      New_N100_ephi0.5_T20_hetereo[[i]]$Maha_wfe_lag.two_coef + New_N100_ephi0.5_T20_hetereo[[i]]$Maha_wfe_lag.two_se * qnorm(.95) > 1) {
    coverage_Maha_wfe_lag.two_N100[i] <- 1
  } else {
    coverage_Maha_wfe_lag.two_N100[i] <- 0
  }
  
}
coverage_Maha_wfe_lag.two_N100 <- percent(mean(coverage_Maha_wfe_lag.two_N100))


coverage_Pscore_wfe_lag.one_N100 <- rep(NA, length(New_N100_ephi0.5_T20_hetereo))
for (i in 1:length(New_N100_ephi0.5_T20_hetereo)) {
  if (New_N100_ephi0.5_T20_hetereo[[i]]$Pscore_wfe_lag.one_coef- New_N100_ephi0.5_T20_hetereo[[i]]$Pscore_wfe_lag.one_se * qnorm(.95) < 1 &
      New_N100_ephi0.5_T20_hetereo[[i]]$Pscore_wfe_lag.one_coef + New_N100_ephi0.5_T20_hetereo[[i]]$Pscore_wfe_lag.one_se * qnorm(.95) > 1) {
    coverage_Pscore_wfe_lag.one_N100[i] <- 1
  } else {
    coverage_Pscore_wfe_lag.one_N100[i] <- 0
  }
  
}
coverage_Pscore_wfe_lag.one_N100 <- percent(mean(coverage_Pscore_wfe_lag.one_N100))


coverage_Pscore_wfe_lag.two_N100 <- rep(NA, length(New_N100_ephi0.5_T20_hetereo))
for (i in 1:length(New_N100_ephi0.5_T20_hetereo)) {
  if (New_N100_ephi0.5_T20_hetereo[[i]]$Pscore_wfe_lag.two_coef- New_N100_ephi0.5_T20_hetereo[[i]]$Pscore_wfe_lag.two_se * qnorm(.95) < 1 &
      New_N100_ephi0.5_T20_hetereo[[i]]$Pscore_wfe_lag.two_coef + New_N100_ephi0.5_T20_hetereo[[i]]$Pscore_wfe_lag.two_se * qnorm(.95) > 1) {
    coverage_Pscore_wfe_lag.two_N100[i] <- 1
  } else {
    coverage_Pscore_wfe_lag.two_N100[i] <- 0
  }
  
}
coverage_Pscore_wfe_lag.two_N100 <- percent(mean(coverage_Pscore_wfe_lag.two_N100))

coverage_ols_N100 <- rep(NA, length(New_N100_ephi0.5_T20_hetereo))
for (i in 1:length(New_N100_ephi0.5_T20_hetereo)) {
  if (New_N100_ephi0.5_T20_hetereo[[i]]$ols_coef- New_N100_ephi0.5_T20_hetereo[[i]]$ols_se * qnorm(.95) < 1 &
      New_N100_ephi0.5_T20_hetereo[[i]]$ols_coef + New_N100_ephi0.5_T20_hetereo[[i]]$ols_se * qnorm(.95) > 1) {
    coverage_ols_N100[i] <- 1
  } else {
    coverage_ols_N100[i] <- 0
  }
  
}
coverage_ols_N100 <- percent(mean(coverage_ols_N100))


# N = 200
coverage_Synth_wfe_lag.one_N200 <- rep(NA, length(New_N200_ephi0.5_T20_hetereo))
for (i in 1:length(New_N200_ephi0.5_T20_hetereo)) {
  if (New_N200_ephi0.5_T20_hetereo[[i]]$Synth_wfe_lag.one_coef- New_N200_ephi0.5_T20_hetereo[[i]]$Synth_wfe_lag.one_se * qnorm(.95) < 1 &
      New_N200_ephi0.5_T20_hetereo[[i]]$Synth_wfe_lag.one_coef + New_N200_ephi0.5_T20_hetereo[[i]]$Synth_wfe_lag.one_se * qnorm(.95) > 1) {
    coverage_Synth_wfe_lag.one_N200[i] <- 1
  } else {
    coverage_Synth_wfe_lag.one_N200[i] <- 0
  }
  
}
coverage_Synth_wfe_lag.one_N200 <- percent(mean(coverage_Synth_wfe_lag.one_N200))


coverage_Synth_wfe_lag.two_N200 <- rep(NA, length(New_N200_ephi0.5_T20_hetereo))
for (i in 1:length(New_N200_ephi0.5_T20_hetereo)) {
  if (New_N200_ephi0.5_T20_hetereo[[i]]$Synth_wfe_lag.two_coef- New_N200_ephi0.5_T20_hetereo[[i]]$Synth_wfe_lag.two_se * qnorm(.95) < 1 &
      New_N200_ephi0.5_T20_hetereo[[i]]$Synth_wfe_lag.two_coef + New_N200_ephi0.5_T20_hetereo[[i]]$Synth_wfe_lag.two_se * qnorm(.95) > 1) {
    coverage_Synth_wfe_lag.two_N200[i] <- 1
  } else {
    coverage_Synth_wfe_lag.two_N200[i] <- 0
  }
  
}
coverage_Synth_wfe_lag.two_N200 <- percent(mean(coverage_Synth_wfe_lag.two_N200))



coverage_Maha_wfe_lag.one_N200 <- rep(NA, length(New_N200_ephi0.5_T20_hetereo))
for (i in 1:length(New_N200_ephi0.5_T20_hetereo)) {
  if (New_N200_ephi0.5_T20_hetereo[[i]]$Maha_wfe_lag.one_coef- New_N200_ephi0.5_T20_hetereo[[i]]$Maha_wfe_lag.one_se * qnorm(.95) < 1 &
      New_N200_ephi0.5_T20_hetereo[[i]]$Maha_wfe_lag.one_coef + New_N200_ephi0.5_T20_hetereo[[i]]$Maha_wfe_lag.one_se * qnorm(.95) > 1) {
    coverage_Maha_wfe_lag.one_N200[i] <- 1
  } else {
    coverage_Maha_wfe_lag.one_N200[i] <- 0
  }
  
}
coverage_Maha_wfe_lag.one_N200 <- percent(mean(coverage_Maha_wfe_lag.one_N200))


coverage_Maha_wfe_lag.two_N200 <- rep(NA, length(New_N200_ephi0.5_T20_hetereo))
for (i in 1:length(New_N200_ephi0.5_T20_hetereo)) {
  if (New_N200_ephi0.5_T20_hetereo[[i]]$Maha_wfe_lag.two_coef- New_N200_ephi0.5_T20_hetereo[[i]]$Maha_wfe_lag.two_se * qnorm(.95) < 1 &
      New_N200_ephi0.5_T20_hetereo[[i]]$Maha_wfe_lag.two_coef + New_N200_ephi0.5_T20_hetereo[[i]]$Maha_wfe_lag.two_se * qnorm(.95) > 1) {
    coverage_Maha_wfe_lag.two_N200[i] <- 1
  } else {
    coverage_Maha_wfe_lag.two_N200[i] <- 0
  }
  
}
coverage_Maha_wfe_lag.two_N200 <- percent(mean(coverage_Maha_wfe_lag.two_N200))


coverage_Pscore_wfe_lag.one_N200 <- rep(NA, length(New_N200_ephi0.5_T20_hetereo))
for (i in 1:length(New_N200_ephi0.5_T20_hetereo)) {
  if (New_N200_ephi0.5_T20_hetereo[[i]]$Pscore_wfe_lag.one_coef- New_N200_ephi0.5_T20_hetereo[[i]]$Pscore_wfe_lag.one_se * qnorm(.95) < 1 &
      New_N200_ephi0.5_T20_hetereo[[i]]$Pscore_wfe_lag.one_coef + New_N200_ephi0.5_T20_hetereo[[i]]$Pscore_wfe_lag.one_se * qnorm(.95) > 1) {
    coverage_Pscore_wfe_lag.one_N200[i] <- 1
  } else {
    coverage_Pscore_wfe_lag.one_N200[i] <- 0
  }
  
}
coverage_Pscore_wfe_lag.one_N200 <- percent(mean(coverage_Pscore_wfe_lag.one_N200))


coverage_Pscore_wfe_lag.two_N200 <- rep(NA, length(New_N200_ephi0.5_T20_hetereo))
for (i in 1:length(New_N200_ephi0.5_T20_hetereo)) {
  if (New_N200_ephi0.5_T20_hetereo[[i]]$Pscore_wfe_lag.two_coef- New_N200_ephi0.5_T20_hetereo[[i]]$Pscore_wfe_lag.two_se * qnorm(.95) < 1 &
      New_N200_ephi0.5_T20_hetereo[[i]]$Pscore_wfe_lag.two_coef + New_N200_ephi0.5_T20_hetereo[[i]]$Pscore_wfe_lag.two_se * qnorm(.95) > 1) {
    coverage_Pscore_wfe_lag.two_N200[i] <- 1
  } else {
    coverage_Pscore_wfe_lag.two_N200[i] <- 0
  }
  
}
coverage_Pscore_wfe_lag.two_N200 <- percent(mean(coverage_Pscore_wfe_lag.two_N200))

coverage_ols_N200 <- rep(NA, length(New_N200_ephi0.5_T20_hetereo))
for (i in 1:length(New_N200_ephi0.5_T20_hetereo)) {
  if (New_N200_ephi0.5_T20_hetereo[[i]]$ols_coef- New_N200_ephi0.5_T20_hetereo[[i]]$ols_se * qnorm(.95) < 1 &
      New_N200_ephi0.5_T20_hetereo[[i]]$ols_coef + New_N200_ephi0.5_T20_hetereo[[i]]$ols_se * qnorm(.95) > 1) {
    coverage_ols_N200[i] <- 1
  } else {
    coverage_ols_N200[i] <- 0
  }
  
}
coverage_ols_N200 <- percent(mean(coverage_ols_N200))

parameters <- c("Synth L = 4", "Synth L = 6", "Maha L = 4", "Maha L =6",
                "Pscore L = 4", "Pscore L = 6", "OLS")
N50 <- c(coverage_Synth_wfe_lag.one_N50, coverage_Synth_wfe_lag.two_N50, 
         coverage_Maha_wfe_lag.one_N50, coverage_Maha_wfe_lag.two_N50,
         coverage_Pscore_wfe_lag.one_N50, coverage_Pscore_wfe_lag.two_N50,
         coverage_ols_N50)

N100 <- c(coverage_Synth_wfe_lag.one_N100, coverage_Synth_wfe_lag.two_N100, 
         coverage_Maha_wfe_lag.one_N100, coverage_Maha_wfe_lag.two_N100,
         coverage_Pscore_wfe_lag.one_N100, coverage_Pscore_wfe_lag.two_N100,
         coverage_ols_N100)

N200 <- c(coverage_Synth_wfe_lag.one_N200, coverage_Synth_wfe_lag.two_N200, 
         coverage_Maha_wfe_lag.one_N200, coverage_Maha_wfe_lag.two_N200,
         coverage_Pscore_wfe_lag.one_N200, coverage_Pscore_wfe_lag.two_N200,
         coverage_ols_N200)

```
We then report coverage rate for 90% CIs. Our WFE regression standard errors tend to overcover quite a bit.  

### Coverage Rate 
```{R, echo = FALSE, cache = TRUE}
table_se <- as.data.frame(cbind(parameters, N50, N100, N200))
library(knitr)
kable(table_se)
```  

A histogram of the 1000 standard errors from synthetic control matching with $L = 4$ and $N = 200$ suggests that our uncertainty estimator does not do anything "weird", as the average standard error is quite small and the standard deviation is not that huge.   

```{R, echo = FALSE, cache = TRUE}
hist(sapply(New_N200_ephi0.5_T20_hetereo, 
            function (x) x$Synth_wfe_lag.one_se),
     main = "SEs for Syntheltic Control with L = 4, N = 200, Beta = 1",
     xlab = "WFE regression standard errors")
```